Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2023-01-27 docs/manuscript/manuscript.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Aggregate Measures Along 4-Dimensions}
A primary aim of our survey was to establish the current level of knowledge and experience geographic researchers have with reproducibility enhancing research practices.
Table 1 presents our summary measures for each topic, as well as those measures by subgroup.

\begin{table}[h]
    \centering
    \begin{threeparttable}
    \caption{Descriptive summary of survey results}
    \begin{tabular}{l c c c c c c c c c c}
         \hline
                    & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & \\
         Measure    & HU & PH & NS & MT            & & QN & QL & MX              & & Overall \\
         \hline
         \textit{DEF}: Definition   &  & & & & & & & & & \\
         Familiarity (\textit{f}) &  \begin{tabular}[c]{@{}c@{}}2.35\\ (1.36)\end{tabular} & 
                        \begin{tabular}[c]{@{}c@{}}3.71\\ (0.98)\end{tabular} & 
                        \begin{tabular}[c]{@{}c@{}}2.28\\ (1.76)\end{tabular} &
                        \begin{tabular}[c]{@{}c@{}}3.97\\ (0.86)\end{tabular} &
                        &
                        \begin{tabular}[c]{@{}c@{}}3.75\\ (0.98)\end{tabular} &
                        \begin{tabular}[c]{@{}c@{}}1.75\\ (1.30)\end{tabular} &
                        \begin{tabular}[c]{@{}c@{}}3.56\\ (1.22)\end{tabular} &
                        &
                        \begin{tabular}[c]{@{}c@{}}3.26\\ (1.36)\end{tabular}\\

@@

%%%%%%%%%%%
\subsubsection*{Definitions and Importance of Reproducibility}
Coded definitions are relative to the NASEM definition. The NASEM state SAME data, procedures, and results and implies SAME context because data is not recollected. 
\begin{itemize}
    \item Self-reported definition (Q6) analysis: Qualitative analysis that will present a typology of definitions by combination of the Q,Q,M and M,P,NS,H splits that match on the 8 category coding of the provided definitions. 
    \item Interpretations (Q8) and Importance (Q17) of reproductions: Develop a split that distinguishes between Qs that focus on epistemology Q8a+Q8b+Q8f+17a, as these provide the most direct information about how a respondent processes the evidence provided by a reproduction; and Qs that focus on reproducibility as a quality of a study Q8e+Q8c+17c+17e+17f. We will explore how these question groups crosstab with the typologies we draw from Q6. Initial assumption is that many will support reproduction as a study characteristic or label, and less will link it with epistomological function. Examine by subfields and methods, which we expect to align with typologies from Q6. 
    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other open science goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
\end{itemize}

In aggregate, respondents identified reproducibility as an important means of achieving numerous epistemic goals in geographic research (Q17).
\begin{itemize}
    \item reducing the risk of persistent errors (77.5\%)
    \item preventing duplication of research efforts (63.3\%)
    \item communicating results to academics (68.8\%)
    \item communicating results to practitioners (64.7\%)
    \item Researchers also view attempting reproductions as an important part of student training (75.7\%). 
\end{itemize}

Qualitative researchers identified reproducibility as playing a much smaller role in the research process when compared to quantitiative or mixed-methods researchers.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Aggregate Measures Along 4-Dimensions}
A primary aim of our survey was to establish how geographic researchers conceptualize reproducibility and their current level of knowledge and experience with reproducibility enhancing research practices.
Nearly all researchers reported being at least somewhat familiar with the term reproducibility (89.0\%) with half reporting being very familiar with the term (53.6\%).
A majority of researchers also believe reproducibility is compatible with epistemologies used in discipline (72.0\%). 
However, researchers estimated that only half of the results published in the discipline were reproducible ($\overline{rep}=50.6\%$, $\sigma=24.7\%$) and reported limited familiarity with and use of many reproducible research practices. 
Few respondents reported attempting to reproduce the work of other researchers (\%) with fewer still attempting to publish those reproduction studies (\%).

Table 1 presents our summary measures for each topic, as well as those measures by subgroup.

\begin{table}[h]
    \centering
    \begin{threeparttable}
    \caption{Descriptive summary of survey results}
    \begin{tabular}{l c c c c c c c c c c}
         \hline
                    & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & \\
         Measure    & HU & PH & NS & MT            & & QN & QL & MX              & & Overall \\
         \hline
         Definition (\textit{d}) & \begin{tabular}[c]{@{}c@{}}1.76\\ (1.17)\end{tabular} & 
                        \begin{tabular}[c]{@{}c@{}}1.68\\ (1.12)\end{tabular} & 
                        \begin{tabular}[c]{@{}c@{}}1.97\\ (1.08)\end{tabular} &
                        \begin{tabular}[c]{@{}c@{}}1.77\\ (1.10)\end{tabular} & 
                        & 
                        \begin{tabular}[c]{@{}c@{}}1.89\\ (1.14)\end{tabular} & 
                        \begin{tabular}[c]{@{}c@{}}1.53\\ (1.28)\end{tabular} & 
                        \begin{tabular}[c]{@{}c@{}}1.78\\ (1.06)\end{tabular} & 
                        & 
                        \begin{tabular}[c]{@{}c@{}}1.77\\ (1.15)\end{tabular} \\
         Familiarity (\textit{f}) &  \begin{tabular}[c]{@{}c@{}}2.35\\ (1.36)\end{tabular} & 
                        \begin{tabular}[c]{@{}c@{}}3.71\\ (0.98)\end{tabular} & 
                        \begin{tabular}[c]{@{}c@{}}2.28\\ (1.76)\end{tabular} &
                        \begin{tabular}[c]{@{}c@{}}3.97\\ (0.86)\end{tabular} &
                        &
                        \begin{tabular}[c]{@{}c@{}}3.75\\ (0.98)\end{tabular} &
                        \begin{tabular}[c]{@{}c@{}}1.75\\ (1.30)\end{tabular} &
                        \begin{tabular}[c]{@{}c@{}}3.56\\ (1.22)\end{tabular} &
                        &
                        \begin{tabular}[c]{@{}c@{}}3.26\\ (1.36)\end{tabular}\\

@@

%%%%%%%%%%%
\subsubsection*{Definitions and Importance of Reproducibility}
Geographic researchers provided definitions of reproducibility that generally explicitly included one to two of the four characteristics ($\overline{d}=1.77$) from the definition adopted by the NASEM.
This level of inclusion was consistent across subfields and methodological approaches.
The availability and use of the same research procedures (80.7\%) and results (74.0\%) were the characteristics of reproducibility most frequently identified by researchers. 
Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
This patterns was also consistent across subfields and approaches, with a slightly greater emphasis on data and procedural consistency and availability amongst quantitative and methods focused researchers.
The lower inclusion of data and context in definitions matched the conflation of reproduction and replication by a minority of researchers (\%).

Researchers defined reproducibility in relation to two epistemic functions.
Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies.
Nearly all other researchers (40.9\%) tied reproducibilty to the need for transparency in research so others could independently expand upon past studies.
Both of these functions were supported by respondents across our sample. 
Overall, a majority of researchers also identified reproducibility as an important for validating (75.2\%) and establishing the credibility (72.5\%) of research.  
Respondents also saw reproducing studies as important to reducing the presence of persistent errors in the discipline (77.5\%) and to increasing trust in research findings (78.45\%).
Matching the emphasis placed on research transparency, respondents identified reproducibility as important to research efficiency (63.3\%) and the communication of findings to academics (68.8\%) and practitioners (64.7\%). 
Half of the respondents (50.9\%) also agreed that when researchers don't share their data they have less trust in a study.
Researchers also view attempting reproductions as an important part of student training (75.7\%).

Despite wide recognition of reproducibility as epistemically important, researchers collectively advocated caution when drawing conclusions from a single reproduction attempts. 
A minority of researchers agreed that an inability to reproduce a result implies that the result is false (26.2\%). 
A larger, but still minority, percentage of researchers believed that an inability to reproduce a result detracts from the validity of a study (41.7\%).

Qualitative researchers identified reproducibility as playing a much smaller role in the research process when compared to the discipline as a whole. 
A majority of the respondents that identified as qualitative researchers believe that reproducibility is incompatible with the epistomologies used in their subfield (75.0\%).
Qualitative researchers did not believe reproducibility to be important to assessing prior work and correcting errors in the literature. 
A small percentage or these respondents agree that reproducibility is important for validating (25.0\%) or establishing the credibility (20.0\%) of qualitative research.
Qualitative geographers similarly placed less emphasis on reproducibility as a means of increasing the accessibility and expansion of research.
Few qualitative researchers had less trust in a study when researchers did not share their data (27.5\%), or saw reproducibility as important to sharing research with academics (27.5\%).
